---
title: "Primary_production_first_try"
author: "Chris Carnivale"
date: "4/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyverse)
require(seacarb)
require(modelr)
require(phytotools)
require(magrittr)
require(ggpubr)
require(lme4)
require(lmerTest)
```

#DIC DYIV Calculation 

Post DIC calculation, then I can do from CPMs to ug of Carbon fixed per hour.

```{r DYIV DIC}
View(carb(flag = 8, 7.3, 0.00097377, S = 0, T = 16))
```

#Carbon Fixation rate calculation

```{r mixo mp PP ugram per L}
mixo_phys_pp <- read.csv("mixo_mp_pp.csv")

str(mixo_phys_pp)

mixo_phys_pp$Time_days <- factor(mixo_phys_pp$Time_days)

mixo_phys_pp$Treatment_plastic <- factor(mixo_phys_pp$Treatment_plastic,levels = c("control", "10","1000", "100000"))

mixo_phy_pp_calc <- mixo_phys_pp %>% mutate(pp_DPM = pp_CPM/C_14_efficiency, bkgr_DPM = background_CPM/C_14_efficiency/0.1, ugram_Cfixed_per_L_hr = pp_DPM*DIC.umol.kg./bkgr_DPM*12*1.029/2)

#0.1 for bckgr_CPM because 0.1 ml was processed
#12 is the molar mass of carbon o convert from umol to ugrams
#1.029 is to convert from kg to L of Seawater
#2 is to get an hourly uptake since it was exposed for 2 hours

ggplot(filter(mixo_phy_pp_calc, !Rep == "A"),aes(x = Treatment_plastic, y = ugram_Cfixed_per_L_hr))+
  geom_boxplot(aes(fill = Time_days))

ggplot(mixo_phy_pp_calc,aes(x = Time_days, y = ugram_Cfixed_per_L_hr))+
  geom_boxplot(aes(fill = Treatment_plastic))

ggplot(filter(mixo_phy_pp_calc, Time_days == "0"),aes(x = Treatment_plastic, y = ugram_Cfixed_per_L_hr))+
  geom_boxplot()

ggplot(filter(mixo_phy_pp_calc, Time_days == "2"),aes(x = Treatment_plastic, y = ugram_Cfixed_per_L_hr))+
  geom_boxplot()

ggplot(filter(mixo_phy_pp_calc, !(Rep == "A" & Treatment_plastic == "control")),aes(x = Time_days, y = ugram_Cfixed_per_L_hr))+
  geom_boxplot(aes(fill = Treatment_plastic))

ggplot(mixo_phy_pp_calc, aes(x = Time_days, y = ugram_Cfixed_per_L_hr))+
  geom_point(aes(color = Treatment_plastic))

#pp_mod1 <- lm(ugram_Cfixed_per_L_hr ~ Time_days + Treatment_plastic, data = mixo_phy_pp_calc)

#pp_mod2 <- lm(ugram_Cfixed_per_L_hr ~ Time_days * Treatment_plastic, data = mixo_phy_pp_calc)

#mod_grid <- mixo_phy_pp_calc %>% 
#  data_grid(Time_days, Treatment_plastic) %>% 
#  gather_predictions()
```

Revisit the model building after I have normalized data. Building a model around
the raw C fixation rates is a waste of time

```{r mixo mp normailize to per cell}
mixo_mp_pp_norm <- mixo_phy_pp_calc %>% 
  mutate(cell_per_L = Cell_counts/1.35*Zeiss_CF*1000, ugram_Cfixed_perCELL_perHR
         = ugram_Cfixed_per_L_hr/cell_per_L,
         pg_perCELL_perHR = ugram_Cfixed_perCELL_perHR*1000000)

str(mixo_mp_pp_norm)



ggplot(mixo_mp_pp_norm, aes(x = Time_days, y = pg_perCELL_perHR))+
  geom_boxplot(aes(fill = Treatment_plastic))

ggplot(filter(mixo_mp_pp_norm, !(Rep == "B" & Treatment_plastic == "control")), aes(x = Time_days, y = pg_perCELL_perHR))+
  geom_boxplot(aes(fill = Treatment_plastic))

ggplot(filter(mixo_mp_pp_norm, Time_days == "0"| Time_days == "2" | Time_days == "4" | Time_days == "7", !(Rep == "B" & Treatment_plastic == "control")),aes(x = Time_days, y = pg_perCELL_perHR))+
  geom_boxplot(aes(fill = Treatment_plastic))

ggplot(filter(mixo_mp_pp_norm, Time_days == "0"| Time_days == "2" | Time_days == "4" | Time_days == "7", !Rep == "B"),aes(x = Time_days, y = pg_perCELL_perHR))+
  geom_boxplot(aes(fill = Treatment_plastic))

ggplot(filter(mixo_mp_pp_norm, Time_days == "0"| Time_days == "2" | Time_days == "4" | Time_days == "7", !(Rep == "B" & Treatment_plastic == "control")),aes(x = Time_days, y = cell_per_L))+
  geom_boxplot(aes(fill = Treatment_plastic))

ggplot(filter(mixo_mp_pp_norm, Time_days == "0"| Time_days == "2" | Time_days == "4" | Time_days == "7", !Rep == "C"),aes(x = Time_days, y = pg_perCELL_perHR))+
  geom_boxplot(aes(fill = Treatment_plastic))

ggplot(filter(mixo_mp_pp_norm, Time_days == "0"| Time_days == "2" | Time_days == "4" | Time_days == "7", !Rep == "D"),aes(x = Time_days, y = pg_perCELL_perHR))+
  geom_boxplot(aes(fill = Treatment_plastic))

ggplot(filter(mixo_mp_pp_norm, Time_days == "0"| Time_days == "2"| Time_days == "4"| Time_days == "7"),aes(x = Time_days, y = cell_per_L))+
  geom_boxplot(aes(fill = Treatment_plastic))
```


```{r mixo mp growth curves}
mixo_mp_abund <- read.csv("mixo_mp_abundance.csv")

mixo_mp_abund$Treatment <- factor(mixo_mp_abund$Treatment,levels = c("Control", "10","1000", "100000"))

mixo_mp_gc <- mixo_mp_abund %>% 
  mutate(cell_per_L = Cell_counts/1.35*Zeiss_CF*1000)

mixo_mp_gc_sum <- mixo_mp_gc %>% 
  group_by(Time_days, Treatment) %>% 
  summarise(avg_cell_per_L = mean(cell_per_L))

ggplot(mixo_mp_gc)+
  geom_point(aes(x = Time_days, y = cell_per_L, color = Treatment))+
  geom_line(data = mixo_mp_gc_sum, aes(x = Time_days, y = avg_cell_per_L, color = Treatment))

#Plotting abundance without Rep B

ggplot(data = filter(mixo_mp_gc, !(Rep == "B" & Treatment == "Control")))+
  geom_point(data = filter(mixo_mp_gc, !(Rep == "B" & Treatment == "Control")), aes(x = Time_days, y = cell_per_L, color = Treatment))+
  geom_line(data = mixo_mp_gc_sum, aes(x = Time_days, y = avg_cell_per_L, color = Treatment))

#need to change the value of the summarised data

mixo_mp_gc_noBcon <- filter(mixo_mp_gc, !(Rep == "B" & Treatment == "Control"))

mixo_mp_gc_sum_noBcon <- mixo_mp_gc_noBcon %>% 
  group_by(Time_days, Treatment) %>% 
  summarise(avg_cell_per_L = mean(cell_per_L))

ggplot(mixo_mp_gc_noBcon)+
  geom_point(aes(x = Time_days, y = cell_per_L, color = Treatment))+
  geom_line(data = mixo_mp_gc_sum_noBcon, aes(x = Time_days, y = avg_cell_per_L, color = Treatment))

```

```{r mixo mp doubling time calc}
#only between days 2-4 after experiment
mixo_mp_DT_data <- filter(mixo_mp_gc_sum, Time_days == "2"| Time_days == "4")

mixo_mp_DT_data1 <- cbind(mixo_mp_DT_data[1:4,1:3],mixo_mp_DT_data[5:8,1:3]) 

mixo_mp_DT_calc <- mixo_mp_DT_data1 %>% mutate(Growth_rate = log(avg_cell_per_L1/avg_cell_per_L)/48, Doubling_time = log(2)/Growth_rate)

ggtexttable(mixo_mp_DT_calc[,c(2,7:8)])

#48 is the number of hours the growth rate is calculated from 

#Now to do it without rep B
mixo_mp_DT_noB_data <- filter(mixo_mp_gc_sum_noBcon, Time_days == "2"| Time_days == "4")

mixo_mp_DT_noB_data1 <- cbind(mixo_mp_DT_noB_data[1:4,1:3],mixo_mp_DT_noB_data[5:8,1:3]) 

mixo_mp_DT_noB_calc <- mixo_mp_DT_noB_data1 %>% mutate(Growth_rate = log(avg_cell_per_L1/avg_cell_per_L)/48, Doubling_time = log(2)/Growth_rate)

ggtexttable(mixo_mp_DT_noB_calc[,c(2,7:8)])

#I am going to attempt to do this from time 0 to peak of all 4 treatments

mixo_mp_DT_data_0to4 <- filter(mixo_mp_gc_sum, Time_days == "0"| Time_days == "4")

mixo_mp_DT_data1_0to4 <- cbind(mixo_mp_DT_data_0to4[1:4,1:3],mixo_mp_DT_data_0to4[5:8,1:3]) 

mixo_mp_DT_calc_0to4 <- mixo_mp_DT_data1_0to4 %>% mutate(Growth_rate = log(avg_cell_per_L1/avg_cell_per_L)/48, Doubling_time = log(2)/Growth_rate)

ggtexttable(mixo_mp_DT_calc_0to4[,c(2,7:8)])

#now wih no rep B
mixo_mp_DT_noB_data_0to4 <- filter(mixo_mp_gc_sum_noBcon, Time_days == "0"| Time_days == "4")

mixo_mp_DT_noB_data1_0to4 <- cbind(mixo_mp_DT_noB_data_0to4[1:4,1:3],mixo_mp_DT_noB_data_0to4[5:8,1:3]) 

mixo_mp_DT_noB_calc_0to4 <- mixo_mp_DT_noB_data1_0to4 %>% mutate(Growth_rate = log(avg_cell_per_L1/avg_cell_per_L)/48, Doubling_time = log(2)/Growth_rate)

ggtexttable(mixo_mp_DT_noB_calc_0to4[,c(2,7:8)])
```

```{r Mixo MP mixed modelling on PP}
mixo_mp_pp_norm_LMM <- lmer(pg_perCELL_perHR ~ Treatment_plastic + (1 + Treatment_plastic|Time_days),
                            data = mixo_mp_pp_norm)

summary(mixo_mp_pp_norm_LMM)

#I think my data follows a nonlinear trend and may be best suited for using
# a log tranformation for a GLMM which could be more suitable.

mixo_mp_pp_norm_GLMM <- glmer(pg_perCELL_perHR ~ Treatment_plastic + (1 + Treatment_plastic|Time_days),
                            data = mixo_mp_pp_norm))
```

```{r Mixo MP Feeding data}
mixo_mp_feed <- read.csv("Mixo_MP_feeding_csv.csv")



mixo_mp_feed_rates <- mixo_mp_feed %>% 
  mutate(bac_conc_perML = bac_avg/bac_micro_filtered*dil_factor*cor_factor_grid,
         micro_conc_perML = micro_avg/bac_micro_filtered*dil_factor*cor_factor_grid,
         BM_ratio = bac_conc_perML/micro_conc_perML,
         BSP_ingested = (conc_bkgrd_per*BM_ratio) + conc_bkgrd_per,
         ing_percell_perhour = BSP_ingested*2)

mixo_mp_feed_rates$Treatment_plastic <- as.factor(mixo_mp_feed_rates$Treatment_plastic)
levels(mixo_mp_feed_rates$Treatment_plastic) <- c("control", "10", "1000","100000")

mixo_mp_feed_rates$Time_days <- as.factor(mixo_mp_feed_rates$Time_days)

ggplot(data = mixo_mp_feed_rates)+
  geom_boxplot(aes(x = Time_days, y = ing_percell_perhour, fill = Treatment_plastic))

boxplot(ing_percell_perhour ~ Time_days*Treatment_plastic, data = mixo_mp_feed_rates)
```

Multiply by 2 b/c feeding was done over 30 mins and we want an hourly rate
Add back in the %ingested initially cause its bacterial size particle ingested


#Arctic PP Work


```{r 2301 PP 12.5% and 50% 6º}
setwd("/Users/christophercarnivale/Desktop/Dissertation_data/Data_from_sarah/")
pp_2301 <- read.csv("PP_2301.csv")

str(pp_2301)

pp_2301$Treatment_light <- factor(pp_2301$Treatment_light)

pp_2301_calc <- pp_2301 %>% mutate(pp_DPM = pp_CPM/C_14_efficiency, bkgr_DPM = background_CPM/C_14_efficiency/0.1, ugram_Cfixed_per_L_hr = pp_DPM*DIC.umol.kg./bkgr_DPM*12*1.029/2)

pp_2301_50 <- read.csv("PP_2301_50.csv")

pp_2301_50$Treatment_light <- factor(pp_2301_50$Treatment_light)

pp_2301_50_calc <- pp_2301_50 %>% mutate(pp_DPM = pp_CPM/C_14_efficiency, bkgr_DPM = background_CPM/C_14_efficiency/0.1, ugram_Cfixed_per_L_hr = pp_DPM*DIC.umol.kg./bkgr_DPM*12*1.029/2)

ep_fit_2301_50 <- fitEP(as.numeric(as.character(pp_2301_50_calc$Treatment_light)), pp_2301_50_calc$ugram_Cfixed_per_L_hr)

mod_par1 <- seq(0,200, by = 1)

Pred_2301_50 <- mod_par/((1/(ep_fit_2301_50[["alpha"]][["Estimate"]]*ep_fit_2301_50[["eopt"]][["Estimate"]]^2))*mod_par^2+(1/ep_fit_2301_50[["ps"]][["Estimate"]]-2/(ep_fit_2301_50[["alpha"]][["Estimate"]]*ep_fit_2301_50[["eopt"]][["Estimate"]]))*mod_par+(1/ep_fit_2301_50[["alpha"]][["Estimate"]]))

Pred_2301_50_df <- as.data.frame(cbind(mod_par1,Pred_2301_50))

pp_2301_50_plot <- ggplot()+
  geom_line(data = Pred_2301_50_df, aes(x = mod_par1,y = Pred_2301_50))+
  geom_point(data = pp_2301_50_calc, aes(x = as.numeric(as.character(Treatment_light)), y = ugram_Cfixed_per_L_hr))

pp_2301_50_plot

str(pp_2301_calc)

ggplot(pp_2301_calc,aes(x = Treatment_light, y = ugram_Cfixed_per_L_hr))+
  geom_boxplot()

ggplot(filter(pp_2301_calc, !Treatment_light == "0"),aes(x = Treatment_light, y = ugram_Cfixed_per_L_hr))+
  geom_boxplot()

ggplot()+
  geom_point(data = pp_2301_50_calc, aes(x = as.numeric(as.character(Treatment_light)), y = ugram_Cfixed_per_L_hr))
    
```

```{r 2290 PP 50% and 12.5% 4º}
setwd("/Users/christophercarnivale/Desktop/Dissertation_data/Data_from_sarah/")
pp_2290 <- read.csv("PP_2290_50.csv")

str(pp_2290)

pp_2290$Treatment_light <- factor(pp_2290$Treatment_light)

pp_2290_calc <- pp_2290 %>% mutate(pp_DPM = pp_CPM/C_14_efficiency, bkgr_DPM = background_CPM/C_14_efficiency/0.1, ugram_Cfixed_per_L_hr = pp_DPM*DIC.umol.kg./bkgr_DPM*12*1.029/2)

pp_2290_125 <- read.csv("PP_2290_125.csv")

pp_2290_125_calc <- pp_2290_125 %>% mutate(pp_DPM = pp_CPM/C_14_efficiency, bkgr_DPM = background_CPM/C_14_efficiency/0.1, ugram_Cfixed_per_L_hr = pp_DPM*DIC.umol.kg./bkgr_DPM*12*1.029/2)

#str(pp_2290_calc)

ggplot(pp_2290_calc,aes(x = Treatment_light, y = ugram_Cfixed_per_L_hr))+
  geom_boxplot()

ggplot(filter(pp_2290_calc, !Treatment_light == "0"),aes(x = Treatment_light, y = ugram_Cfixed_per_L_hr))+
  geom_boxplot()

pp_2290_4C_50_point_plot <- ggplot(pp_2290_calc,aes(x = Treatment_light, y = ugram_Cfixed_per_L_hr))+
  geom_point()+
  ylab("")+
  xlab("")+
  ylim(0,6)

pp_2290_4C_125_point_plot <- ggplot(pp_2290_125_calc,aes(x = Treatment_light, y = ugram_Cfixed_per_L_hr))+
  geom_point()+
  ylab("")+
  xlab("")+
  ylim(0,6)

#fitEP(pp_2290_calc) it needs an x and y vectors and not a datafram

fitEP(x = pp_2290_calc$Treatment_light,y = pp_2290_calc$ugram_Cfixed_per_L_hr)
#That doesn't work

#data("rlcs")
#iew(rlcs)

#A single RLC from Rep A

pp_2290_single_RLC <- filter(pp_2290_calc, Rep == "A")

ep_fit <- fitEP(as.numeric(as.character(pp_2290_single_RLC$Treatment_light)), pp_2290_single_RLC$ugram_Cfixed_per_L_hr)

#as.double(pp_2290_single_RLC$Treatment_light)

#droplevels(pp_2290_single_RLC$Treatment_light)
#both of the above didn't work to convert from factor to number

as.numeric(as.character(pp_2290_single_RLC$Treatment_light))

ep_fit

#plot(ep_fit)

mod_par <- seq(0,200, by = 1)
with(ep_fit,{
P <- mod_par/((1/(alpha[1]*eopt[1]^2))*mod_par^2+(1/ps[1]-2/(alpha[1]*eopt[1]))*mod_par+(1/alpha[1]))
plot.new()+
plot(mod_par,P, type = "l")
})

Pred <- mod_par/((1/(ep_fit[["alpha"]][["Estimate"]]*ep_fit[["eopt"]][["Estimate"]]^2))*mod_par^2+(1/ep_fit[["ps"]][["Estimate"]]-2/(ep_fit[["alpha"]][["Estimate"]]*ep_fit[["eopt"]][["Estimate"]]))*mod_par+(1/ep_fit[["alpha"]][["Estimate"]]))

#P

plot(pp_2290_single_RLC$Treatment_light, pp_2290_single_RLC$ugram_Cfixed_per_L_hr, type = "p") 

#plot(mod_par,P, type = "l")

EP_mod_data <- as.data.frame(cbind(mod_par, Pred))

ggplot()+
  geom_line(data = EP_mod_data, aes(x = mod_par,y = Pred))+
  geom_point(data = pp_2290_single_RLC, aes(x = as.numeric(as.character(Treatment_light)), y = ugram_Cfixed_per_L_hr))


pp_2290_calc_ord <- arrange(pp_2290_calc, Rep)

id <- unique(pp_2290_calc$Rep)

n <- length(id)

alpha <-  array(NA, c(n,4))
eopt <-  array(NA, c(n,4))
ps <-  array(NA, c(n,4))
ssr <-  array(NA, c(n,4))
Residuals <-  array(NA, c(n,4))

PAR1 <- array(NA, c(n,4))
C_fixed1 <- array(NA, c(n,4))

for(i in 1:n){
  PAR <- as.numeric(as.character(pp_2290_calc_ord$Treatment_light[pp_2290_calc_ord$Rep == id[i]]))
  C_fixed <- pp_2290_calc_ord$ugram_Cfixed_per_L_hr[pp_2290_calc_ord$Rep == id[i]]
  
  PP_fit <- fitEP(PAR, C_fixed, normalize = TRUE)
#normalized parameters for comparison to other 
  alpha[i,] <- PP_fit$alpha
  eopt[i,] <- PP_fit$eopt
  ps[i,] <- PP_fit$ps
  ssr[i,] <- PP_fit$ssr
  Residuals[i,] <- PP_fit$residuals
  
}

for(i in 1:n){
  PAR <- as.numeric(as.character(pp_2290_calc_ord$Treatment_light[pp_2290_calc_ord$Rep == id[i]]))
  C_fixed <- pp_2290_calc_ord$ugram_Cfixed_per_L_hr[pp_2290_calc_ord$Rep == id[i]]
  
  PP_fit <- fitEP(PAR, C_fixed, normalize = FALSE)
#non normalized parameters
  alpha[i,] <- PP_fit$alpha
  eopt[i,] <- PP_fit$eopt
  ps[i,] <- PP_fit$ps
  ssr[i,] <- PP_fit$ssr
  Residuals[i,] <- PP_fit$residuals
  
  }

for(i in 1:n){
  PAR1[i,] <- as.numeric(as.character(pp_2290_calc_ord$Treatment_light[pp_2290_calc_ord$Rep == id[i]]))
  C_fixed1[i,] <- pp_2290_calc_ord$ugram_Cfixed_per_L_hr[pp_2290_calc_ord$Rep == id[i]]
  #This is a check to make sure my for loop is indaxing properly
}



#nls(formula = ugram_Cfixed_per_L_hr ~ Pmax * ((2*(2+b)*Treatment_light/opt_light)/((Treatment_light/opt_light)^2+2*b*Treatment_light/opt_light+1)), 
            #data = pp_2290_single_RLC, 
            #start = list(opt_light = 100, Pmax = 5.6581134, b = 0.5))
#nls() wasn't working and I'm not sure why but I don't need it when I can use
#phytotools package to do the same exact thing

#Prior I have plotted the prediction of the single RLC model

#Next chunk is model to the average of the 4 reps


pp_2290_sum <- pp_2290_calc %>% 
  group_by(Treatment_light) %>% 
  summarise(avg_ugram_per_L_per_HR = mean(ugram_Cfixed_per_L_hr))

ep_fit_50 <- fitEP(as.numeric(as.character(pp_2290_sum$Treatment_light)), pp_2290_sum$avg_ugram_per_L_per_HR)

Pred_2290 <- mod_par/((1/(ep_fit_50[["alpha"]][["Estimate"]]*ep_fit_50[["eopt"]][["Estimate"]]^2))*mod_par^2+(1/ep_fit_50[["ps"]][["Estimate"]]-2/(ep_fit_50[["alpha"]][["Estimate"]]*ep_fit_50[["eopt"]][["Estimate"]]))*mod_par+(1/ep_fit_50[["alpha"]][["Estimate"]]))

Pred_2290_df <- as.data.frame(cbind(mod_par,Pred_2290))

ggplot()+
  geom_line(data = Pred_2290_df, aes(x = mod_par,y = Pred_2290))+
  geom_point(data = pp_2290_calc, aes(x = as.numeric(as.character(Treatment_light)), y = ugram_Cfixed_per_L_hr))

#trying to get model for all 4 reps at once

ep_fit_4rep <- fitEP(as.numeric(as.character(pp_2290_calc$Treatment_light)), pp_2290_calc$ugram_Cfixed_per_L_hr)

ep_fit_4rep

Pred_2290_4rep <- mod_par/((1/(ep_fit_4rep[["alpha"]][["Estimate"]]*ep_fit_4rep[["eopt"]][["Estimate"]]^2))*mod_par^2+(1/ep_fit_4rep[["ps"]][["Estimate"]]-2/(ep_fit_4rep[["alpha"]][["Estimate"]]*ep_fit_4rep[["eopt"]][["Estimate"]]))*mod_par+(1/ep_fit_4rep[["alpha"]][["Estimate"]]))

Pred_2290_4rep_df <- as.data.frame(cbind(mod_par,Pred_2290))

pp_2290_50_plot <- ggplot()+
  geom_line(data = Pred_2290_4rep_df, aes(x = mod_par,y = Pred_2290))+
  geom_point(data = pp_2290_calc, aes(x = as.numeric(as.character(Treatment_light)), y = ugram_Cfixed_per_L_hr))+xlab("Light Intensity")+ylab("ugrams_Cfixed_perhour")

#Plot for 2290 12.5%

ep_fit_125 <- fitEP(as.numeric(as.character(pp_2290_125_calc$Treatment_light)), pp_2290_125_calc$ugram_Cfixed_per_L_hr)

ep_fit_125

Pred_2290_125 <- mod_par/((1/(ep_fit_125[["alpha"]][["Estimate"]]*ep_fit_125[["eopt"]][["Estimate"]]^2))*mod_par^2+(1/ep_fit_125[["ps"]][["Estimate"]]-2/(ep_fit_125[["alpha"]][["Estimate"]]*ep_fit_125[["eopt"]][["Estimate"]]))*mod_par+(1/ep_fit_125[["alpha"]][["Estimate"]]))

Pred_2290_125_df <- as.data.frame(cbind(mod_par,Pred_2290_125))

pp_2290_125_plot <- ggplot()+
  geom_line(data = Pred_2290_125_df, aes(x = mod_par,y = Pred_2290_125))+
  geom_point(data = pp_2290_125_calc, aes(x = as.numeric(as.character(Treatment_light)), y = ugram_Cfixed_per_L_hr))

ggarrange(pp_2290_50_plot,pp_2290_125_plot)

```

```{r PP 2290 50, 12.5 at 6C}
setwd("/Users/christophercarnivale/Desktop/Dissertation_data/Data_from_sarah/")
pp_2290_6C_50 <- read.csv("PP_2290_50_6C.csv")

str(pp_2290_6C_50)

pp_2290_6C_50$Treatment_light <- factor(pp_2290_6C_50$Treatment_light)

pp_2290_6C_50_calc <- pp_2290_6C_50 %>% mutate(pp_DPM = pp_CPM/C_14_efficiency, bkgr_DPM = background_CPM/C_14_efficiency/0.1, ugram_Cfixed_per_L_hr = pp_DPM*DIC.umol.kg./bkgr_DPM*12*1.029/2)

pp_2290_6C_50_pointplot <- ggplot(pp_2290_6C_50_calc,aes(x = Treatment_light, y = ugram_Cfixed_per_L_hr))+
  geom_point()+
  ylab("")+
  xlab("")+
  ylim(0,6)

pp_2290_6C_125 <- read.csv("PP_2290_125_6C.csv")

str(pp_2290_6C_125)

pp_2290_6C_125$Treatment_light <- factor(pp_2290_6C_125$Treatment_light)

pp_2290_6C_125_calc <- pp_2290_6C_125 %>% mutate(pp_DPM = pp_CPM/C_14_efficiency, bkgr_DPM = background_CPM/C_14_efficiency/0.1, ugram_Cfixed_per_L_hr = pp_DPM*DIC.umol.kg./bkgr_DPM*12*1.029/2)

pp_2290_6C_125_pointplot <- ggplot(pp_2290_6C_125_calc,aes(x = Treatment_light, y = ugram_Cfixed_per_L_hr))+
  geom_point()+
  ylab("")+
  xlab("")+
  ylim(0,6)

pp_2290_6C_125_pointplot

ggarrange(pp_2290_6C_125_pointplot,pp_2290_6C_50_pointplot)

PP_2290_4and6 <- ggarrange(pp_2290_4C_50_point_plot,pp_2290_6C_50_pointplot, pp_2290_4C_125_point_plot, pp_2290_6C_125_pointplot, labels = c("A", "B", "C", "D"))

annotate_figure(PP_2290_4and6,
                top = "P vs I curves of Dinobryon at 4ªC and 6ªC",
                left = "Carbon Fixation Rate (ug/Lhr)",
                bottom = "A and C are 4ªC              B and D are 6ªC")
```

```{r running mixo_mp_controlrun}
mixo_mp_pp_controlrun <- read.csv("/Users/christophercarnivale/Desktop/Dissertation_data/Microplastic_physiological_response/mixo_mp_pp_controlrun.csv")

mixo_mp_pp_controlrun_calc <- mixo_mp_pp_controlrun %>% mutate(pp_DPM = pp_CPM/C_14_efficiency, bkgr_DPM = background_CPM/C_14_efficiency/0.1, ugram_Cfixed_per_L_hr = pp_DPM*DIC.umol.kg./bkgr_DPM*12*1.029/2)

ggplot(mixo_mp_pp_controlrun_calc, aes(x = Treatment_plastic, y = ugram_Cfixed_per_L_hr))+
  geom_boxplot()
```


